Comparison of MCMC algorithms in Stochastic Volatility Models

### 2023-09-24 manuscript/main.tex
updated location
fixed references

\documentclass[12pt, a4paper]{article}
\setcounter{tocdepth}{2}
\usepackage{graphicx} % Required for inserting images
\usepackage[parfill]{parskip} % Removes indent from new paragraphs
\usepackage{amsmath, amssymb, amsfonts}
\usepackage[colorlinks = true,
			citecolor  = blue]{hyperref}

\usepackage[longnamesfirst,authoryear, round]{natbib}
\bibliographystyle{unsrtnat}

@@

        Generating 1000 samples of $h_2^{sim}$ from both centered and non-centered models gives samples from the same data generating process as shown in figure x.

        \begin{figure}[h]
            \centering
            \includegraphics[scale=0.1]{ppc_h2.png}
            \caption{Prior predictive samples of second state variable}
        \end{figure}

@@

% \bibliographystyle{apa} % Econometrica referencing
\bibliography{references}

>>>>

\documentclass[12pt, a4paper]{article}
\setcounter{tocdepth}{2}
\usepackage{graphicx} % Required for inserting images
\usepackage[parfill]{parskip} % Removes indent from new paragraphs
\usepackage{amsmath, amssymb, amsfonts}
\usepackage[colorlinks = true,
			citecolor  = blue,
            linkcolor = black]{hyperref}

\usepackage[natbibapa]{apacite}
\bibliographystyle{apacite}
% \usepackage[longnamesfirst,authoryear, round]{natbib}
% \bibliographystyle{unsrtnat}

@@

        Generating 1000 samples of $h_2^{sim}$ from both centered and non-centered models gives samples from the same data generating process as shown in figure 3.

        \begin{figure}[h]
            \centering
            \includegraphics[scale=0.1]{figures/ppc_h2.png}
            \caption{Prior predictive samples of second state variable}
        \end{figure}

@@

\bibliography{references}
